---
title: "Final Data Product"
author: "KJ Sherman"
date: "August 16, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Table of Contents
- Description of the app
- Application
- Data used in the application
- Links 

## Description of Application
This application leverages the "quakes" dataset in Rstudio which is based on recorded information from earthquakes in Fiji in 1964. The application lets the user create different bins to organize the data. These bins create groupings of the recorded depths of the earthquakes. The graph then displays the frequency in which the depth of these earthquakes falls within different ranges.

## Application

<iframe src="https://kjsherman.shinyapps.io/finalproject/" style="border: none; width: 700px; height: 700px"></iframe>

## Dataset
```{r quakes, echo = TRUE}
head(quakes)
```

## Links
shiny app
https://kjsherman.shinyapps.io/finalproject/

github repo
https://github.com/kjsherman/dataProductsProject
